Capstone Movielens Report

### 2025-05-15 reports/capstone-movielens.site/04.appendix.Rmd
Report, Appendix updated: function `union_cv_results` described.

# Appendix {#appendix.a}

@@

#### Sugnature
\
```{r eval=FALSE}
tune.model_param <- function(param_values, 
                             fn_tune.test.param_value, 
                             break.if_min = TRUE,
                             steps.beyond_min = 2){

@@

#### Sugnature
\
```{r eval=FALSE}
model.tune.param_range <- function(loop_starter,
                             tune_dir_path,
                             cache_file_base_name,
                             fn_tune.test.param_value,
                             max.identical.min_RMSE.count = 4,
                             endpoint.min_diff = 0,
                             break.if_min = TRUE,
                             steps.beyond_min = 2){
  # ...
  list(best_result = param_values.best_result,
       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
       tuned.result = data.frame(parameter.value = parameter.value,
                                 RMSE = result.RMSE))
}
```

@@

#### Sugnature
\
```{r eval=FALSE}
get_fine_tune.param.endpoints.idx <- function(preset.result) {
  # ...

@@

#### Sugnature
\
```{r eval=FALSE}
get_best_param.result <- function(param_values, rmses){
  # ...

@@

### [func.00]() Function {#func.00}
\

::: { #func.00.signature .sidebar }
#### Sugnature
\

@@

::: { #func.00.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.00.details .sidebar }
#### Details
\

@@

::: { #func.00.value .sidebar }
#### Value
\

@@

::: { #func.00.code .sidebar }
#### Source Code
\

The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func]() Function {#func.01}
\

::: { #func.01.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.01.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.01.details .sidebar }
#### Details
\

@@

::: { #func.01.value .sidebar }
#### Value
\

@@

::: { #func.01.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func]() Function {#func.02}
\

::: { #func.02.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.02.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.02.details .sidebar }
#### Details
\

@@

::: { #func.02.value .sidebar }
#### Value
\

@@

::: { #func.02.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func.0]() Function {#func.0}
\

::: { #func.0.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.0.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.0.details .sidebar }
#### Details
\

@@

::: { #func.0.value .sidebar }
#### Value
\

@@

::: { #func.0.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

### [func1]() Function {#func.03}
\

::: { #func.03.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

::: { #func.03.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

::: { #func.03.details .sidebar }
#### Details
\

::: { #func.03.value .sidebar }
#### Value
\

::: { #func.03.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func1]() Function {#func.1}
\

::: { #func.1.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.1.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.1.details .sidebar }
#### Details
\

@@

::: { #func.1.value .sidebar }
#### Value
\

@@

::: { #func.1.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func.2]() Function {#func.2}
\

::: { #func.2.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.2.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.2.details .sidebar }
#### Details
\

@@

::: { #func.2.value .sidebar }
#### Value
\

@@

::: { #func.2.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func.3]() Function {#func.3}
\

::: { #func.3.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.3.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.3.details .sidebar }
#### Details
\

@@

::: { #func.3.value .sidebar }
#### Value
\

@@

::: { #func.3.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func.4]() Function {#func.4}
\

::: { #func.4.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.4.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.4.details .sidebar }
#### Details
\

@@

::: { #func.4.value .sidebar }
#### Value
\

@@

::: { #func.4.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func.5]() Function {#func.5}
\

::: { #func.5.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.5.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.5.details .sidebar }
#### Details
\

@@

::: { #func.5.value .sidebar }
#### Value
\

@@

::: { #func.5.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func.6]() Function {#func.6}
\

::: { #func.6.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.6.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.6.details .sidebar }
#### Details
\

@@

::: { #func.6.value .sidebar }
#### Value
\

@@

::: { #func.6.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func.7]() Function {#func.7}
\

::: { #func.7.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.7.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.7.details .sidebar }
#### Details
\

@@

::: { #func.7.value .sidebar }
#### Value
\

@@

::: { #func.7.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [func.8]() Function {#func.8}
\

::: { #func.8.signature .sidebar }
#### Sugnature
\
```{r eval=FALSE}

@@

::: { #func.8.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.8.details .sidebar }
#### Details
\

@@

::: { #func.8.value .sidebar }
#### Value
\

@@

::: { #func.8.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### []() Function {#func.3-1}
\

#### Sugnature
\
```{r eval=FALSE}

#### Parameters
\
  - **fn_tune.test.param_value:** A helper function that calculates the value of the `RMSE` for a given parameter value.; 
  - **break.if_min = TRUE:** A Boolean parameter that determines whether the function should terminate after completing the number of steps specified by the parameter `steps.beyond_min`, after the minimum value of the `RMSE` has been found;
  - **steps.beyond_min = 2:** (takes effect only if `break.if_min` parameter is `TRUE`) Specifies the number of steps after finding the minimum value of the `RMSE`, upon completion of which the function should terminate.

::: {.noteblock data-latex=""}
Note 
:::

#### Value
\

#### Source Code
\
Below is the most significant part of the code of the [function]() function:
```{r eval=FALSE}

================================================================================

```
::: {.noteblock data-latex=""}
!!! Note!
:::

See the `func.model.tune.param_range` Function description [above](#func.model.tune.param_range).

::: {.noteblock data-latex=""}
Note 
:::

::: {.noteblock data-latex=""}
Note 
:::

::: {.noteblock data-latex=""}
!!! Note!
:::

::: {.noteblock data-latex=""}
!!! Note!
:::

::: {.noteblock data-latex=""}
!!! Note!
:::

s

>>>>

# Appendix {#appendix.a}
## Data Helper Functions
\

### [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) Function {#func.union_cv_results}
\

Aggregates the input data frames into a single data frame.

::: { #func.union_cv_results.Usage .sidebar }
#### Usage
\

```{r eval=FALSE}
union_cv_results(data_list = data)

::: { #func.union_cv_results.params .sidebar }
#### Parameters
\
::: { #func.mean_reg.params.data_list .sidebar }
  - **data_list:** List of data frames representing the results of the _N-Fold Cross Validation_ method execution.;

:::
:::

::: { #func.union_cv_results.details .sidebar }
#### Details
\

The function is used to aggregate the _N-Fold Cross Validation_ method result data into a single data frame for further processing.

::: { #func.union_cv_results.value .sidebar }
#### Value
\

A data frame that is a union of the input data frames.
:::

::: { #func.union_cv_results.code .sidebar }
#### Source Code
\

The soure code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) function is shown below:
```{r eval=FALSE}
union_cv_results <- function(data_list) {
  out_dat <- data_list[[1]]

  for (i in 2:CVFolds_N){
    out_dat <- union(out_dat, 
                     data_list[[i]])
  }

  out_dat
}
```

::: {.noteblock data-latex=""}
The source code of the [union_cv_results](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) is also available in the [Model training](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L431) section of the [data.helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/data.helper.functions.R#L432) script.
:::
:::

@@

#### Signature
\
```{r eval=FALSE}
tune.model_param <- function(param_values, 
                             fn_tune.test.param_value, 
                             break.if_min = TRUE,
                             steps.beyond_min = 2){

@@

#### Signature
\
```{r eval=FALSE}
model.tune.param_range <- function(loop_starter,
                             tune_dir_path,
                             cache_file_base_name,
                             fn_tune.test.param_value,
                             max.identical.min_RMSE.count = 4,
                             endpoint.min_diff = 0,
                             break.if_min = TRUE,
                             steps.beyond_min = 2){
  # ...
  list(best_result = param_values.best_result,
       param_values.endpoints = c(prm_val.leftmost, prm_val.rightmost, seq_increment),
       tuned.result = data.frame(parameter.value = parameter.value,
                                 RMSE = result.RMSE))
}
```

@@

#### Signature
\
```{r eval=FALSE}
get_fine_tune.param.endpoints.idx <- function(preset.result) {
  # ...

@@

#### Signature
\
```{r eval=FALSE}
get_best_param.result <- function(param_values, rmses){
  # ...

@@

### [fname00]() Function {#func.fname00}
\

::: { #func.fname00.Usage .sidebar }
#### Usage
\

@@

::: { #func.fname00.params .sidebar }
#### Parameters
\
::: { #func.mean_reg.params.param1s .sidebar }
  - **param1:** description;

:::
::: { #func.mean_reg.params.param2 .sidebar }
  - **param2:** description.

:::
:::

::: { #func.fname00.details .sidebar }
#### Details
\

::: { #func.fname00.value .sidebar }
#### Value
\

@@

::: { #func.fname00.code .sidebar }
#### Source Code
\

The soure code of the [fname00]() function is shown below:
```{r eval=FALSE}

::: {.noteblock data-latex=""}
The source code of the [fname00]() is also available in the [Some.Section]() section of the [Somefunctions.R]() script.
:::
:::

### [fname01]() Function {#func.fname01}
\

::: { #func.fname01.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

::: { #func.fname01.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

::: { #func.fname01.details .sidebar }
#### Details
\

@@

::: { #func.fname01.value .sidebar }
#### Value
\

@@

::: { #func.fname01.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname02]() Function {#func.fname02}
\

::: { #func.fname02.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname02.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname02.details .sidebar }
#### Details
\

@@

::: { #func.fname02.value .sidebar }
#### Value
\

@@

::: { #func.fname02.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname0]() Function {#func.fname0}
\

::: { #func.fname0.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname0.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname0.details .sidebar }
#### Details
\

@@

::: { #func.fname0.value .sidebar }
#### Value
\

@@

::: { #func.fname0.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname03]() Function {#func.fname03}
\

::: { #func.fname03.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname03.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname03.details .sidebar }
#### Details
\

@@

::: { #func.fname03.value .sidebar }
#### Value
\

@@

::: { #func.fname03.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname1]() Function {#func.fname1}
\

::: { #func.fname1.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname1.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname1.details .sidebar }
#### Details
\

@@

::: { #func.fname1.value .sidebar }
#### Value
\

@@

::: { #func.fname1.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname2]() Function {#func.fname2}
\

::: { #func.fname2.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname2.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname2.details .sidebar }
#### Details
\

@@

::: { #func.fname2.value .sidebar }
#### Value
\

@@

::: { #func.fname2.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname3]() Function {#func.fname3}
\

::: { #func.fname3.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname3.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname3.details .sidebar }
#### Details
\

@@

::: { #func.fname3.value .sidebar }
#### Value
\

@@

::: { #func.fname3.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname4]() Function {#func.fname4}
\

::: { #func.fname4.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname4.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname4.details .sidebar }
#### Details
\

@@

::: { #func.fname4.value .sidebar }
#### Value
\

@@

::: { #func.fname4.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname5]() Function {#func.fname5}
\

::: { #func.fname5.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname5.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname5.details .sidebar }
#### Details
\

@@

::: { #func.fname5.value .sidebar }
#### Value
\

@@

::: { #func.fname5.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname6]() Function {#func.fname6}
\

::: { #func.fname6.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname6.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname6.details .sidebar }
#### Details
\

@@

::: { #func.fname6.value .sidebar }
#### Value
\

@@

::: { #func.fname6.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname7]() Function {#func.fname7}
\

::: { #func.fname7.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname7.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname7.details .sidebar }
#### Details
\

@@

::: { #func.fname7.value .sidebar }
#### Value
\

@@

::: { #func.fname7.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@

### [fname8]() Function {#func.fname8}
\

::: { #func.fname8.signature .sidebar }
#### Signature
\
```{r eval=FALSE}

@@

::: { #func.fname8.params .sidebar }
#### Parameters
\
  - **param1:** description; 
  - **param2:** description.

@@

::: { #func.fname8.details .sidebar }
#### Details
\

@@

::: { #func.fname8.value .sidebar }
#### Value
\

@@

::: { #func.fname8.code .sidebar }
#### Source Code
\
The soure code of the [function]() function is shown below:
```{r eval=FALSE}

@@
